---
title: "R Notebook"
output: html_notebook
---
```{r error=FALSE, message=FALSE, warning=FALSE, results=}
library(dplyr)
library(clustree)
library(Seurat)
library(patchwork)
library(plyr)
library(magrittr)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(fs)
library(roxygen2)
library(utils)
library(fs)
library(knitr)
library(purrr)
library(reshape)
library(ggplot2)
library(matlab)
library(matrixStats)
library(cowplot)
library(openxlsx)
library(readxl)
library(harmony)
library(SoupX)
#library(DoubletFinder)
library(ggpubr)
library(pheatmap)
#library(dittoSeq)
library(scales)
library(gridExtra)
library(stargazer)
library(data.table)
library(rmarkdown)
library(monocle3)
library(monocle)
library(SeuratWrappers)
library(monocle3)
library(monocle)
library(pheatmap)
library(gprofiler2)
library(stringr)
library(RColorBrewer)
library(moonBook)
library(ggforce)
library(yarrr)
library(clustree)
library(scCustomize)


set.seed(1) 

 basic.marker1 <- c( "Lepr", "Cemip", "Mag", "Pdgfra", "Gfap", "Slc1a2", "Ptprc", "Syt1", "Nrg1", "รง", "Cux2", 'S100a8','Gad1', 'Slc17a7', 'Flt1', "Mbp", 'Plp1','Tmem119', 'P2ry12', 'Trem2', 'Itgam', 'Itgax', 'Mecom', 'Pdgfrb', 'Acta2', 'Apoe', 'Top2a', 'Enpp6', 'Cspg4','Cd14')

colorsp.new <- colorRampPalette(paste0('#',c("f7b99b","e88da0","73c9e8","b1d29d","f9d28b","72b6e4")))
 
 color.match <- colorRampPalette(paste0('#',c("f7bba1","e99ca4","b2aec6","8fccd6","b5d5a3","e7d597"))) ## Use this for L1 object
 
 color.test <- colorRampPalette(paste0('#',c("E6735A","3d5467","779fa1","FCDE9C","564154","af5d63"))) ## Use this for MIC object
 
 `%notin%` <- Negate(`%in%`)
 
 draw_colnames_45 <- function (coln, gaps, ...) {
    coord <- pheatmap:::find_coordinates(length(coln), gaps)
    x     <- coord$coord - 0.5 * coord$size
    res   <- grid::textGrob(
      coln, x = x, y = unit(1, "npc") - unit(3,"bigpts"),
      vjust = 0.75, hjust = 1, rot = 45, gp = grid::gpar(...)
    )
    return(res)
}
assignInNamespace(
  x = "draw_colnames",
  value = "draw_colnames_45",
  ns = asNamespace("pheatmap")
)

OneDrive_PDF.PNG <- function(p.name){
  ggsave(filename = paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/3_plots.output/2_PDF/OLIG/',
                         p.name,'_',
                         format(Sys.Date(), "%Y%m%d"),
                         '.PDF'),
       limitsize = F)  

  
  ggsave(filename = paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/3_plots.output/1_PNG/OLIG/',
                         p.name,'_',
                         format(Sys.Date(), "%Y%m%d"),
                         '.png'),
       limitsize = F)  
}

`%notin%` <- Negate(`%in%`)

```

# Functions for dotplots and feature plots split by a category with titles
```{r}

FPlist <- function(seuratobj,genes){
    FeaturePlot_scCustom(seuratobj, genes ,num_columns = n.col,colors_use  = c('grey90',paste0('#',c("4FB3AA","e9d8a6","ee9b00","ae2012"))),pt.size = 0.05, order = order.input) & NoAxes() 
} #function to plot markers for each cluster 


DPlist <- function(seuratobj,genes,resolution){
   DotPlot(seuratobj,features=genes,group.by = resolution, dot.scale = 6,cluster.idents = F,col.max = 1.5, col.min = -1.5)+
    theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
  scale_colour_gradient2(low = "#046A83", mid = "white",high = '#D26952',midpoint = 0) + theme_light()  + 
  rotate_x_text(60) +
    theme( plot.margin = margin(b = 0, r = 20),
          legend.position = 'right',
          axis.title.x = element_text(size = 0),
          axis.title.y = element_text(size = 0)) +
    geom_point(aes(size = pct.exp), alpha = 0.25, shape = 21, color="black", stroke = 0.75)+
  FontSize(x.text = 12,y.text = 12) + coord_flip()
} #function to plot markers for each cluster 
```
# Function to remove duplicated gene names from a list of markers from findmarkers 
```{r}
rmDup <- function(list.of.genes){
 df <- bind_rows(list.of.genes, .id = 'Cluster') #convert list to a df, list name elements go to Cluster column
 df$Cluster <- as.factor(df$Cluster) # make factor for reassigning names after split
df$gene <- gsub(pattern = "\\.\\.\\.(.+)", x = rownames(df), replacement = '') #remove text after gene name for duplicated marker, store in new col called gene
df <- df[which(isUnique(df$gene) == T),] # subset the df for only unique genes
list <- split(df,df$Cluster ) # split back into a list by the Cluster col
names(list) <- levels(df$Cluster) #reassign names using Cluster levels

list.genes <- lapply(list, rownames) # make list with just gene names 

list.out <- list(list,list.genes)
names(list.out) <- c('List','List.genes') # Output is a list of two different lists: (1) List with original formatting containing expression info and (2) List with only gene names split by cluster

list.out
}
```
# Function to remove duplicated gene names from a list from findmarkers, prepare a paged table display, and save it as a csv 
```{r}
markers.to.exp <- function(list.of.markers.to.export,file.name){
  list.of.markers.to.export_rownames <- lapply(list.of.markers.to.export, rownames)

list.of.markers.to.export <- bind_rows(list.of.markers.to.export, .id = 'Cluster') %>% #merge list of markers into one dataframe, new column for cluster number
  setorder(-avg_logFC) #sort by average log FC
paged_table(list.of.markers.to.export) # display table

list.of.markers.to.export$gene <- gsub(pattern = "\\.\\.\\.(.+)", x = rownames(list.of.markers.to.export), replacement = '') #remove text after gene name for duplicated marker

if (exists(file.name) == T){
write.table(markers.toexport, 
            paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_', file.name,'_',
            format(Sys.Date(), "%Y%m%d"),
            '.csv'),
            append= F, 
            sep=',',
            row.names = TRUE,
            col.names = NA)
} else{'No filename given, did not save csv'}

list.of.markers.to.export
}
```
# QC plot function
```{r fig.height=7, fig.width=12}

QCplot <- function(seuratobj,resolution){
  colorsp.new <- colorRampPalette(paste0('#',c("f7b99b","e88da0","73c9e8","b1d29d","f9d28b","72b6e4")))
  
  count <- VlnPlot(seuratobj,feature = "nCount_RNA",group.by = resolution,pt.size =0,ncol = 1,cols = colorsp.new(length(levels(seuratobj@meta.data[[resolution]])))) + theme(text = element_text(size = 12)) + stat_summary(fun = median, fun.min = median, fun.max = median,geom = "crossbar", width = 0.5) #+ ylim(c(0 ,30000))
mt <- VlnPlot(seuratobj,feature = "percent.mt",group.by = resolution,pt.size =0,ncol = 1,cols = colorsp.new(length(levels(seuratobj@meta.data[[resolution]])))) + theme(text = element_text(size = 12)) + stat_summary(fun = median, fun.min = median, fun.max = median,geom = "crossbar", width = 0.5) + ylim(c(0 ,15))
feat <- VlnPlot(seuratobj,feature = "nFeature_RNA",group.by = resolution,pt.size =0,ncol = 1,cols = colorsp.new(length(levels(seuratobj@meta.data[[resolution]])))) + theme(text = element_text(size = 12)) + stat_summary(fun = median, fun.min = median, fun.max = median,geom = "crossbar", width = 0.5) #+ ylim(c(0 ,3000))

(count / mt / feat) & NoLegend() | DimPlot(object = seuratobj,reduction = "umap", pt.size = .25, group.by = resolution ,label = TRUE,label.size = 5,cols =colorsp.new(length(levels(seuratobj@meta.data[[resolution]]))))  + labs(title = paste0(resolution))+ theme_void() + NoLegend()
}


```


---

## Read RDS
```{r}
IMM <- readRDS('/Users/brakeam/Library/CloudStorage/OneDrive-NationalInstitutesofHealth/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/Cleaned/IMM_all_cleaned_20220427.RDS')
```


```{r fig.height=8, fig.width=18}
DimPlot(IMM)
DimPlot(IMM, split.by = 'IL08_condition.7',pt.size = 0.05,ncol = 4) & NoAxes()
```

# Subset T2T3 only
```{r}
IMM_T2T3_T1234umap <- subset(IMM, subset = IL08_condition.6 %in% c("T2_Peak","T3_Recovery"), invert = FALSE)
```
# Basic seurat pipeine
```{r}
set.seed(0)
# IMM_T2T3 <- IMM_T2T3_T1234umap   %>%
#     PercentageFeatureSet(pattern = "^mt-", col.name = "percent.mt") %>%
#     NormalizeData(normalization.method = "LogNormalize",verbose = FALSE,scale.factor = 10000) %>%
#     FindVariableFeatures(selection.method = "vst", nfeatures = 3000) %>%
#     ScaleData(verbose = FALSE) %>%
#     RunPCA(npcs = 50, verbose = FALSE) %>%
#     RunHarmony("IL01_uniqueID", plot_convergence = TRUE) %>%
#     RunUMAP(reduction = "harmony", dims = 1:6, min.dist=0.001, spread = 5,n.components = 2) %>% #1:5
#     FindNeighbors(reduction = "harmony", dims = 1:6) %>% #1:5
#     FindClusters(resolution = c(0.2, 0.3, 0.6, 0.8, 1.0, 1.2, 1.6)) %>%
#     identity()


IMM_T2T3 <- readRDS('/Users/brakeam/Library/CloudStorage/OneDrive-NationalInstitutesofHealth/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/PreCleaning_T2T3/IMM_T2T3_20240726.RDS')
   
```
# Dimplot with various grouping
```{r fig.height=9, fig.width=15}
(DimPlot(IMM_T2T3, group.by = 'IL15_annotation.res0.6.short2') | DimPlot(IMM_T2T3, group.by = 'RNA_snn_res.0.2') |DimPlot(IMM_T2T3, group.by = 'RNA_snn_res.0.3')) / (DimPlot(IMM_T2T3, group.by = 'RNA_snn_res.0.6') | DimPlot(IMM_T2T3, group.by = 'RNA_snn_res.0.8') | DimPlot(IMM_T2T3, group.by = 'RNA_snn_res.1'))
```
# Transfer labels from IMM to IMM_T2T3
```{r Transfer clustering labels from IMM to T2T3, fig.height=15, fig.width=15}

index <- match(colnames(IMM_T2T3),colnames(IMM)) #match(source)

#Is index the right size? yes 
length(index) == length(colnames(IMM_T2T3))#TRUE

# Does the index reflect the position of each cell from the subset in the merged object? yes
test <- colnames(IMM_T2T3) == colnames(IMM)[index] 
which(test == 'FALSE') #all true 

#transfer labels
IMM_T2T3$IMM_IL15_annotation.res0.6.short2 <- 'temp'
IMM_T2T3$IMM_IL15_annotation.res0.6.short2 <-  as.character(IMM$IL15_annotation.res0.6.short2)[index]

#Was transfer successful? 

  ## yes all counts match up
table(IMM_T2T3$IMM_IL15_annotation.res0.6.short2) #Merged object
table(IMM$IL15_annotation.res0.6.short2) #Labels that were transferred in the subset object

  ## are the correct cells labeled?
test <- IMM_T2T3$IMM_IL15_annotation.res0.6.short2[index] == IMM$IL15_annotation.res0.6.short2 # are those cells given the same name in both objects?
which(test == 'FALSE') #all true 

# Convert back to a factor
IMM_T2T3$IMM_IL15_annotation.res0.6.short2 <- as.factor(IMM_T2T3$IMM_IL15_annotation.res0.6.short2)

(DimPlot(IMM_T2T3, group.by = "IMM_IL15_annotation.res0.6.short2") + labs(title = 'IMM_IL15_annotation.res0.6.short2'))/ (DimPlot(IMM_T2T3, group.by = "IL15_annotation.res0.6.short2", label = T, repel = T)+ labs(title = 'IL15_annotation.res0.6.short2')) 

DimPlot(IMM_T2T3, split.by = "IL15_annotation", group.by ="IMM_IL15_annotation.res0.6.short2" , label = F, repel = T,ncol = 5) 
```
# Basic Marker Featureplot
```{r fig.height=15, fig.width=15}
FeaturePlot(IMM_T2T3, basic.marker1, order = T, ncol = 5,cols = c('grey90',paste0('#',c("4FB3AA","e9d8a6","ee9b00","ae2012")))) 
```
# QC plot
```{r fig.height=4, fig.width=6}
QCplot(IMM_T2T3, resolution = 'RNA_snn_res.0.6')
```

---


---

# Markers
## Find Markers res.0.3
```{r Find markers}
# Idents(IMM_T2T3) <- IMM_T2T3$RNA_snn_res.0.3
# 
# clusters <- as.list(levels(Idents(IMM_T2T3)))
# 
# #find markers
# markers_T2T3_res0.3 <- lapply(clusters, FindMarkers,object = IMM_T2T3)
# names(markers_T2T3_res0.3) <- paste0('RNA_snn_res.0.3_c',levels(Idents(IMM_T2T3))) #rename the list items to match the cluster numbers
# markers_T2T3_res0.3
# 
# ### Save marker data
#  saveRDS(markers_T2T3_res0.3, '/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_AllMarkers_Res0.3_20240614.rds')
# 
# write.xlsx(markers_T2T3_res0.3,  paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/AST/11_ASTReanalysis/AST_T2T3_AllMarkers_Res0.3_',
#  #           format(Sys.Date(), "%Y%m%d"),
#  #           '.xlsx'), rowNames = TRUE)
 
########################################## Read marker data ########################################## 
 markers_T2T3_res0.3 <-  readRDS('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/AST/AST_T2T3_AllMarkers_Res0.3_20240501.rds')
```

## Find Markers res.0.6
```{r Find markers}
Idents(IMM_T2T3) <- IMM_T2T3$RNA_snn_res.0.6

clusters <- as.list(levels(Idents(IMM_T2T3)))

#find markers
markers_T2T3_res0.6 <- lapply(clusters, FindMarkers,object = IMM_T2T3)
names(markers_T2T3_res0.6) <- paste0('RNA_snn_res.0.6_c',levels(Idents(IMM_T2T3))) #rename the list items to match the cluster numbers
markers_T2T3_res0.6

### Save marker data
 saveRDS(markers_T2T3_res0.6, paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_AllMarkers_Res0.6_',
           format(Sys.Date(), "%Y%m%d"),'.rds'))

write.xlsx(markers_T2T3_res0.6,  paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_AllMarkers_Res0.6_',
           format(Sys.Date(), "%Y%m%d"),
            '.xlsx'), rowNames = TRUE)
 
########################################## Read marker data ########################################## 
#markers_T2T3_res0.3 <-  readRDS('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/AST/AST_T2T3_AllMarkers_Res0.6_20240910.rds')
```

## Find Markers res.0.6 c0 vs 2
```{r Find markers}
Idents(IMM_T2T3) <- IMM_T2T3$RNA_snn_res.0.6

clusters <- as.list(levels(Idents(IMM_T2T3)))

#find markers
markers_T2T3_res0.6_c0v2 <- FindMarkers(object = IMM_T2T3, ident.1 = 0, ident.2 = 2) %>% list()
names(markers_T2T3_res0.6_c0v2) <- paste0('RNA_snn_res.0.6_c',c('0vs2')) #rename the list items to match the cluster numbers
markers_T2T3_res0.6_c0v2

### Save marker data
 saveRDS(markers_T2T3_res0.6_c0v2, paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_AllMarkers_Res0.6_c0v2',
           format(Sys.Date(), "%Y%m%d"),'.rds'))

write.xlsx(markers_T2T3_res0.6_c0v2,  paste0('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3_AllMarkers_Res0.6_c0v2',
           format(Sys.Date(), "%Y%m%d"),
            '.xlsx'), rowNames = TRUE)
 
########################################## Read marker data ########################################## 
#markers_T2T3_res0.6_c0v2 <-  readRDS('')
```

### Feature plot
```{r plot top10 markers for each cluster, fig.height=4, fig.width=20}
top10_markers <- lapply(markers_T2T3_res0.6_c0v2, filter, pct.1 <0.5, pct.2 >0.5) # filter by upper and lower cutoff for pct1 and pct2

# use apply to select top 10 markers from each list item
#top10_markers <-  lapply(markers_T2T3_res0.6, head, 60)

#markers.to.exp(top10_markers_res0.3,'top10_markers_res0.3')

top10_markers.toplot <- rmDup(top10_markers)

## FEATURE PLOT ##
n.col = 6
order.input <- T

fp <- lapply(seuratobj = IMM_T2T3, X = top10_markers.toplot[[2]], FUN = FPlist)

rel.height <- ceil(as.numeric(lapply(top10_markers.toplot, length))/n.col) 

p.name <- 'FeaturePlot_IMMT2T3_RNA_snn_res.0.6' # to use for export

plot_grid(plotlist = fp, ncol = 1, rel_heights = rel.height, labels = paste0('Cluster ', names(fp)), label_colour = '#ae2012', vjust = 1.05, label_size = 16, scale = 0.95) #merge plots for all clusters into one big figure for export
 
top10_markers.toplot[[2]]

```
### Dotplot
```{r fig.height=15, fig.width=8}
## DOT PLOT ##
resolution = 'RNA_snn_res.0.6'

dp <- lapply(seuratobj = IMM_T2T3, X = top10_markers.toplot[[2]], DPlist, resolution = resolution)

#rel.height <- as.numeric(lapply(top10_markers.toplot[[2]], length)) #take the expected number of rows and based on length of markers for each cluster and the number of columns

p.name <- 'FeaturePlot_IMMT2T3_RNA_snn_res.0.6_top10' # to use for export
 plot_grid(plotlist = dp, ncol = 1, rel_heights = 1, labels = paste0('Cluster ', names(dp)), label_colour = '#ae2012', vjust = 1.0, label_size = 16, scale = 0.85, axis = 'l') #merge plots for all clusters into one big figure for export

```
### Plot all markers 
```{r fig.height=9, fig.width=5}

genes <- plyr::ldply(top10_markers_res0.3.toplot[[2]],cbind)
colnames(genes) <- c('Cluster','Gene')
genes <- genes$Gene

resolution <- 'RNA_snn_res.0.6'
  
 DotPlot(IMM_T2T3,features=genes,group.by = resolution, dot.scale = 6,cluster.idents = F,col.max = 1.5, col.min = -1.5)+
    theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
  scale_colour_gradient2(low = "#046A83", mid = "white",high = '#D26952',midpoint = 0) + theme_light()  + 
  rotate_x_text(60) +
    theme( plot.margin = margin(b = 0, r = 20),
          legend.position = 'right',
          axis.title.x = element_text(size = 0),
          axis.title.y = element_text(size = 0)) +
    geom_point(aes(size = pct.exp), alpha = 0.25, shape = 21, color="black", stroke = 0.75)+
  FontSize(x.text = 12,y.text = 12) + coord_flip()
```

## Actrims markers
```{r fig.height=30, fig.width=15}
ACTRIMS.markers <- c('Cd8a','Skap1','Gm2682','Ccl5','Ms4a4b','Kcnip4','Lsamp','Snhg11','Fgf14','Top2a','Diaph3','Kif11','Knl1','Myo1e','Igf1','Gpnmb', 'Xylt1', 'Ifi213','Gm4951', 'Slfn5', 'Ifi207','Fth1','Tyrobp', 'C1qa', 'Apoe', 'Csmd3','Gm10791', 'Siglech', 'P3h2','Sgcz', 'Gm47271', 'Tusc3', 'Cdh4', 'Cst3', 'Tmem119', 'Selplg', 'P2ry12', 'Nrxn3', 'Meis2', 'Sox2ot', 'Auts2', 'Lyz2', 'Cd63')

markers <- c('Fgf13', 'Lyst', 'Itgax','Fth1','Fau' ,'Siglech', 'P2ry12','Selplg', 'Grp34', 'Nav3', 'Cst3','Ptprc', 'Itgam', 'Cspg4', 'Trem2' ,'Syt1' , 'Top2a' ,'Nrxn1','Cadm2','Lsamp','Pcdh9','Cntnap2','Ptprd'  , 'Ezh2','Tmpo' ,'Cd74','H2-Ab1','H2-Aa','H2-Eb1' ,'Themis','Nkg7','Grap2','Cd226','H2-Q7','Skap1','Ltb','Ms4a4b','Gm2682','Bcl2' )

 FeaturePlot(IMM_T2T3, ACTRIMS.markers ,ncol = n.col,cols = c('grey90',paste0('#',c("4FB3AA","e9d8a6","ee9b00","ae2012"))),pt.size = 0.05,order = T) & NoAxes() 
  FeaturePlot(IMM_T2T3, markers ,ncol = n.col,cols = c('grey90',paste0('#',c("4FB3AA","e9d8a6","ee9b00","ae2012"))),pt.size = 0.05,order = F) & NoAxes() 
```

# Save object
```{r}
saveRDS(IMM_T2T3,'/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/PreCleaning_T2T3/IMM_T2T3_20240726.RDS' ) # This object is pre-manual doublet removal

IMM_T2T3 <- readRDS('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/PreCleaning_T2T3/IMM_T2T3_20240726.RDS')
```

--- 
# Remove res0.6 cluster 11 (see mapmycells) **(IMM_T2T3.sub)**

## Subset 
```{r}
#IMM_T2T3.sub <- subset(IMM_T2T3, RNA_snn_res.0.6 %in% c(11) ,invert = T )
IMM_T2T3.sub <- readRDS('/Users/brakeam/Library/CloudStorage/OneDrive-NationalInstitutesofHealth/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/Cleaned_T2T3only/IMM_T2T3_cleaned_20240804.RDS')
```
## Basic seurat pipeine
```{r}
# IMM_T2T3.sub <- IMM_T2T3.sub   %>%
#     PercentageFeatureSet(pattern = "^mt-", col.name = "percent.mt") %>%
#     NormalizeData(normalization.method = "LogNormalize",verbose = FALSE,scale.factor = 10000) %>%
#     FindVariableFeatures(selection.method = "vst", nfeatures = 3000) %>%
#     ScaleData(verbose = FALSE) %>%
#     RunPCA(npcs = 50, verbose = FALSE) %>%
#     RunHarmony("IL01_uniqueID", plot_convergence = TRUE) %>%
#     RunUMAP(reduction = "harmony", dims = 1:8, min.dist=0.001, spread = 5,n.components = 2) %>% #1:5
#     FindNeighbors(reduction = "harmony", dims = 1:8) %>% #1:5
#     FindClusters(resolution = c(0.2, 0.3, 0.6, 0.7, 0.8, 1.0, 1.2, 1.6)) %>% #0.2, 0.3, 0.6, 0.8, 1.0, 1.2, 1.6
#     identity()
```
## Dim plot multiple resolutions
```{r fig.height=3, fig.width=12}
DimPlot(IMM_T2T3.sub, group.by = 'IL15_annotation.res0.6.short2') + labs(title = 'IL15_annotation.res0.6.short2')| DimPlot(IMM_T2T3.sub, group.by = 'RNA_snn_res.0.6',label = T) + labs(title = 'RNA_snn_res.0.6') | DimPlot(IMM_T2T3.sub, group.by = 'RNA_snn_res.0.8',label = T)+ labs(title = 'RNA_snn_res.08') | DimPlot(IMM_T2T3.sub, group.by = 'RNA_snn_res.1') + labs(title = 'RNA_snn_res.1')
```
## Transfer labels from IMM_T2T3 sub to the ACTRIMS object (IMM)
```{r Transfer clustering labels from IMM_T2T3.sub to ACTRIMS (T1-T4) object, fig.height=4, fig.width=8}

index <- match(colnames(IMM),colnames(IMM_T2T3.sub)) #match(source)

#Is index the right size? yes 
length(index) == length(colnames(IMM))#TRUE

# Does the index reflect the position of each cell from the subset in the merged object? yes
test <- colnames(IMM) == colnames(IMM_T2T3.sub)[index] 
which(test == 'FALSE') #all true 

#transfer labels
IMM$IMM_IL15_annotation.T2T3.res0.6 <- 'T1/T4'
IMM$IMM_IL15_annotation.T2T3.res0.6 <-  as.character(IMM_T2T3.sub$RNA_snn_res.0.6)[index]

#Was transfer successful? 

  ## yes all counts match up
table(IMM_T2T3.sub$RNA_snn_res.0.6) #T2T3 object
table(IMM$IMM_IL15_annotation.T2T3.res0.6) #Labels that were transferred in the ACTRIMS object

## are the correct cells labeled?
test <- IMM$IMM_IL15_annotation.T2T3.res0.6 == IMM_T2T3.sub$RNA_snn_res.0.6[index] # are those cells given the same name in both objects?
which(test == 'FALSE') #all true 

IMM.plot <- subset(IMM,subset = IMM_IL15_annotation.T2T3.res0.6 %in% levels(IMM_T2T3.sub$RNA_snn_res.0.6),invert = F)

# Convert back to a factor
IMM.plot$IMM_IL15_annotation.T2T3.res0.6 <- as.factor(IMM.plot$IMM_IL15_annotation.T2T3.res0.6)

(DimPlot(IMM.plot, group.by = "IMM_IL15_annotation.T2T3.res0.6") + labs(title = 'IMM_IL15_annotation.T2T3.res0.6')) | (DimPlot(IMM_T2T3.sub, group.by = "RNA_snn_res.0.6", label = T, repel = T)+ labs(title = 'RNA_snn_res.0.6')) 
```

## Feature plot old res0.3 markers
```{r}
## FEATURE PLOT ##
n.col = 2 
order.input <- T

fp <- lapply(seuratobj = IMM_T2T3.sub, X = top10_markers_res0.3.toplot[[2]], FUN = FPlist)

rel.height <- ceil(as.numeric(lapply(top10_markers_res0.3.toplot, length))/n.col) 

p.name <- 'FeaturePlot_ASTT2T3_RNA_snn_res.0.3_top10' # to use for export

plot_grid(plotlist = fp, ncol = 3, rel_heights = rel.height, labels = paste0('Cluster ', names(fp)), label_colour = '#ae2012', vjust = 1.05, label_size = 16, scale = 0.95) #merge plots for all clusters into one big figure for export
 
```

## ACTRIMS markers on subset obj
### Feature plot ACTRIMS markers
```{r fig.height=13, fig.width=10}
n.col = 4
order.input = T
FPlist(genes = ACTRIMS.markers, seuratobj = IMM_T2T3.sub )
```
### Dotplot ACTRIMS markers
```{r fig.height=9, fig.width=4}
DPlist(genes = ACTRIMS.markers, seuratobj = IMM_T2T3.sub, resolution = 'IL15_annotation.res0.6.short2' )
```

# Feature plot JP EAE markers
```{r fig.height=14, fig.width=10}
JP_EAE_markers <- c('Tmem150c','Sell','Cd36','Tshr','Slco4c1','Slco6a1','Cd36','Il17ra','Arhgap33','Pdk4','Pdgfc','Cd36','Wars','Mrc1','Ccser1','Slco5a1','Ccr7','Cpvl','Irf8','Osbpl10','Eaf2','Ece1','Ace','Frmpd','Skap1','Itgam','Itgax','Ptprg','Il2ra','Ctla4','Il7r','Lef1','Klrk1','Klrd1','Flt1','Ifi203')

n.col = 4
order.input = T
FPlist(genes = JP_EAE_markers, seuratobj = IMM_T2T3.sub )
```

# Various dimplots with split
```{r fig.height=10, fig.width=10}
(DimPlot(IMM_T2T3, split.by = "IL08_condition.8", group.by ="RNA_snn_res.0.6" , label = T, repel = T,ncol = 4) + NoAxes() + labs(title = 'IMM_T2T3')) / (DimPlot(IMM_T2T3.sub, split.by = "IL08_condition.8", group.by ="RNA_snn_res.0.6" , label = T, repel = T,ncol = 4) + NoAxes()+ labs(title = 'IMM_T2T3.sub'))

(DimPlot(IMM_T2T3, split.by = "IL08_condition.8", group.by ="IL15_annotation.res0.6.short2" , label = F, repel = T,ncol = 4)  + NoAxes()+ labs(title = 'IMM_T2T3'))/ (DimPlot(IMM_T2T3.sub, split.by = "IL08_condition.8", group.by ="IL15_annotation.res0.6.short2" , label = F, repel = T,ncol = 4)  + NoAxes()+ labs(title = 'IMM_T2T3.sub'))
```

# Transfer clustering labels from IMM_T2T3 to IMM_T2T3.sub
```{r Transfer clustering labels from IMM to T2T3, fig.height=10, fig.width=13}

index <- match(colnames(IMM_T2T3.sub),colnames(IMM_T2T3)) #match(source)

#Is index the right size? yes 
length(index) == length(colnames(IMM_T2T3.sub))#TRUE

# Does the index reflect the position of each cell from the subset in the merged object? yes
test <- colnames(IMM_T2T3.sub) == colnames(IMM_T2T3)[index] 
which(test == 'FALSE') #all true 

#transfer labels
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_IMM_T2T3_presub')

IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTE <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTE <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_',str_pad(as.character(IMM_T2T3.sub$RNA_snn_res.0.6)[index], 2, pad = "0"))

IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTEres7 <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTEres7 <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_',str_pad(as.character(IMM_T2T3.sub$RNA_snn_res.0.7)[index], 2, pad = "0"))


#Was transfer successful? 

  ## yes all counts match up
table(IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset) #Merged object
table(IMM_T2T3$RNA_snn_res.0.7) #Labels that were transferred in the subset object

  ## are the correct cells labeled?
test <- IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset== IMM_T2T3$RNA_snn_res.0.6[index]  # are those cells given the same name in both objects?
which(test == 'FALSE') #all true 

# Convert back to a factor
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <- as.factor(IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset)

((DimPlot(IMM_T2T3.sub, group.by = "IMM_IL15_annotation.res0.6.presubset",label = F) + labs(title = 'IMM_IL15_annotation.res0.6.presubset'))| (DimPlot(IMM_T2T3, group.by = "RNA_snn_res.0.6", label = T, repel = T)+ labs(title = 'RNA_snn_res.0.6')) )/((DimPlot(IMM_T2T3.sub, group.by = "IMM_IL15_annotation.res0.6.short2") + labs(title = 'IMM_IL15_annotation.res0.6.short2'))| (DimPlot(IMM_T2T3, group.by = "IMM_IL15_annotation.res0.6.short2", label = F, repel = T)+ labs(title = 'IMM_IL15_annotation.res0.6.short2')) )
```

## Determine where each annotation tracks in comparison to ACTRIMS annotation in the new object
```{r}
DimPlot(IMM_T2T3.sub, group.by ="IMM_IL15_annotation.res0.6.presubsetPASTEres7" , label = F, repel = T,ncol = 1) + NoLegend()

table(IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTEres7)


library(dplyr)
table <- IMM_T2T3.sub@meta.data %>%
    group_by(IMM_IL15_annotation.res0.6.short2,IMM_IL15_annotation.res0.6.presubsetPASTEres7,RNA_snn_res.0.7) %>%
    dplyr::summarize(count=n()) %>%
  as.data.frame()

list <- split(table,table$IMM_IL15_annotation.res0.6.short2)
lapply(list, function(x) x[order(-x$count), ]) 


library(dplyr)
table <- IMM_T2T3.sub@meta.data %>%
    group_by(IMM_IL15_annotation.res0.6.short2,RNA_snn_res.0.7) %>%
    dplyr::summarize(count=n()) %>%
  as.data.frame()

list <- split(table,table$IMM_IL15_annotation.res0.6.short2)
lapply(list, function(x) x[order(-x$count), ]) 


```

--- 

# FindMarkers 0.6 
## Find Markers res.0.6
```{r Find markers}
Idents(IMM_T2T3.sub) <- IMM_T2T3.sub$RNA_snn_res.0.6

clusters <- as.list(levels(Idents(IMM_T2T3.sub)))
markers_T2T3_res0.6 <- lapply(clusters, FindMarkers,object = IMM_T2T3.sub)
names(markers_T2T3_res0.6) <- paste0('RNA_snn_res.0.6_c',levels(Idents(IMM_T2T3.sub))) #rename the list items to match the cluster numbers

markers_T2T3_res0.6

### Save marker data 
saveRDS(markers_T2T3_res0.6, '/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3sub_AllMarkers_Res0.6_20240802.rds')
 
########################################## Read marker data ########################################## 
#markers_T2T3_res0.6 <-  readRDS('/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/IMM_T2T3sub_AllMarkers_Res0.6_20240802.rds)
```
## plot top10 markers for each cluster res0.6
```{r plot top10 markers for each cluster, fig.height=30, fig.width=10}
#markers.to.exp(top10_markers_res0.3,'top10_markers_res0.3')

# use apply to select top 10 markers from each list item
top10_markers_res0.6 <-  lapply(markers_T2T3_res0.6, head, 10)

top10_markers_res0.6.toplot <- rmDup(top10_markers_res0.6)

## FEATURE PLOT ##
n.col = 5 ####
order.input <- T ####
p.name <- 'FeaturePlot_ASTT2T3_RNA_snn_res.0.6_top10' # to use for export ####

fp <- lapply(seuratobj = IMM_T2T3.sub, X = top10_markers_res0.6.toplot[[2]], FUN = FPlist) ####

rel.height <- ceil(as.numeric(lapply(top10_markers_res0.6.toplot[[2]], length))/n.col) 
plot_grid(plotlist = fp, ncol = 1, rel_heights = rel.height, labels = paste0(names(fp)), label_colour = '#ae2012', vjust = 1.05, label_size = 12, scale = 0.95) #merge plots for all clusters into one big figure for export
```
### Dotplot
```{r fig.height=12, fig.width=15}
## DOT PLOT ##

p.name <- 'FeaturePlot_IMMT2T3.sub_RNA_snn_res.0.6_top10' ##### to use for export

dp <- lapply(seuratobj = IMM_T2T3.sub, X = top10_markers_res0.6.toplot[[2]], DPlist,resolution = 'RNA_snn_res.0.6') #####

plot_grid(plotlist = dp, ncol = 3, labels = paste0(names(dp)), label_colour = '#ae2012', vjust = 1.0, label_size = 16, scale = 0.85, axis = 'l') #merge plots for all clusters into one big figure for export
```
### Plot all markers 
```{r fig.height=12, fig.width=4}

genes <- plyr::ldply(top10_markers_res0.6.toplot[[2]],cbind) #####
colnames(genes) <- c('Cluster','Gene')
genes <- genes$Gene

 
DPlist(seuratobj = IMM_T2T3.sub,genes = genes,resolution <- 'RNA_snn_res.0.6')

```

# QC plot
```{r}
QCplot(seuratobj = IMM_T2T3.sub,resolution = 'RNA_snn_res.0.6')
```

# Markers from pre-sub object
```{r}
n.col = 3
order.input = T
FPlist(seuratobj = IMM_T2T3, genes = c('Gm10790', 'mt-Co2,', 'Ifi203', 'Snhg11','Top2a','Sox11','Fmn1'))
FPlist(seuratobj = IMM_T2T3, genes = c('Apoe', 'Igf1', 'Lilrb4', 'Lyz2', 'Colec12', 'Msr1',  'Map1lc3b')) #  shown to be part of the phagocytic signature in adult cerebellar microglia 
```

# Plot markers from MapMyCells run (pre subset)

## Plot markers for the classes and subclasses identified 
## use both subclass.markers.combo and subclass.tf.markers.combo

```{r}
OBIMN.GABA.45 <- unique(dput(scan(text="2610307P16Rik,Dlx1,Zeb2,Pax6,Dlx2,Zeb2,Bcl11b,Meis2,Nfix", what=",", sep = ',')))
CB.Granule.GLUT.314 <- unique(dput(scan(text="Gabra6,Ror1,Pax6,Neurod2,Etv1", what=",", sep = ',')))
ASTRO.NT.NN.318 <- unique(dput(scan(text="Aqp4,Cd38,Agt,Itih3,Rfx4,Dbx2,Prdm16,Nr2f1", what="", sep = ',')))
Microglia.NN.318 <- unique(dput(scan(text="C1qa,Tmem119,Fli1,Sall1", what=",", sep = ','))) 
BAM.NN.335 <- unique(dput(scan(text="Mrc1,Maf,Fli1,Etv1,Runx1,Trps1", what=",", sep = ','))) 
DC.NN.337 <- unique(dput(scan(text="Cd74,Runx1,Batf3", what="", sep = ','))) 
Lymphoid.NN.338 <- unique(dput(scan(text="Cd52,Gimap3,Ikzf1,Ikzf3", what=",", sep = ','))) 

# make a list with all of them 
Allen.marker.list <- list(OBIMN.GABA.45,CB.Granule.GLUT.314,ASTRO.NT.NN.318,Microglia.NN.318,BAM.NN.335,DC.NN.337,Lymphoid.NN.338) 
  names(Allen.marker.list) <-  dput(scan(text="OBIMN.GABA.45,CB.Granule.GLUT.314,ASTRO.NT.NN.318,Microglia.NN.318,BAM.NN.335,DC.NN.337,Lymphoid.NN.338", what="", sep = ','))
  
genes <- plyr::ldply(Allen.marker.list,cbind)
colnames(genes) <- c('subclass','Gene') 
genes <- genes[which(isUnique(genes$Gene) == T),] # subset the df for only unique genes
rownames(genes) <- genes$Gene

Allen.marker.list.unique <- split(genes,genes$subclass)
Allen.marker.list.unique <- lapply(Allen.marker.list.unique, rownames)
```

## Plot allen markers from mapmycells top subclasses
```{r fig.height=14, fig.width=8}
order.input = T
n.col = 4
fp <- lapply(seuratobj = IMM_T2T3.sub, X = Allen.marker.list.unique, FUN = FPlist)
rel.height <- ceil(as.numeric(lapply(Allen.marker.list.unique, length))/n.col) 

plot_grid(plotlist = fp, ncol = 1, rel_heights = rel.height, labels = paste0(names(fp)), label_colour = '#ae2012', vjust = 1.05, label_size = 16, scale = 0.95) #merge plots for all clusters into one big figure for export
```
```{r fig.height=8, fig.width=12}
dp <- lapply(seuratobj = IMM_T2T3.sub, X = Allen.marker.list.unique, FUN = DPlist, resolution = 'RNA_snn_res.0.6' )
rel.height <- as.numeric(lapply(Allen.marker.list.unique, length)) #take the expected number of rows and based on length of markers for each cluster and the number of columns
 plot_grid(plotlist = dp, ncol = 3, labels = paste0(names(dp)), label_colour = '#ae2012', vjust = 1.0, label_size = 16, scale = 0.85, axis = 'l') #merge plots for all clusters into one big figure for export
```

# Export IMM_T2T3.sub which is the reclustered object with res0.6 cluster removed
```{r}
saveRDS(IMM_T2T3.sub,'/Users/brakeam/OneDrive - National Institutes of Health/JP & Alexis/20240419_newDTA/1_data.input/1_DTA/Cleaned/IMM_T2_cleaned_20240804.RDS')
```

# Transfer labels from  IMM_T2T3 to IMM_T2T3.sub
```{r Transfer clustering labels from IMM to T2T3, fig.height=7, fig.width=10}

index <- match(colnames(IMM_T2T3.sub),colnames(IMM_T2T3)) #match(source)

#Is index the right size? yes 
length(index) == length(colnames(IMM_T2T3.sub))#TRUE

# Does the index reflect the position of each cell from the subset in the merged object? yes
test <- colnames(IMM_T2T3.sub) == colnames(IMM_T2T3)[index] 
which(test == 'FALSE') #all true 

#transfer labels
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_IMM_T2T3_presub')

IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTE <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTE <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_',str_pad(as.character(IMM_T2T3.sub$RNA_snn_res.0.6)[index], 2, pad = "0"))

IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTEres7 <- ''
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubsetPASTEres7 <-  paste0(str_pad(as.character(IMM_T2T3$RNA_snn_res.0.6)[index], 2, pad = "0"),'_',str_pad(as.character(IMM_T2T3.sub$RNA_snn_res.0.7)[index], 2, pad = "0"))


#Was transfer successful? 

  ## yes all counts match up
table(IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset) #Merged object
table(IMM_T2T3$RNA_snn_res.0.7) #Labels that were transferred in the subset object

  ## are the correct cells labeled?
test <- IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset== IMM_T2T3$RNA_snn_res.0.6[index]  # are those cells given the same name in both objects?
which(test == 'FALSE') #all true 

# Convert back to a factor
IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset <- as.factor(IMM_T2T3.sub$IMM_IL15_annotation.res0.6.presubset)

((DimPlot(IMM_T2T3.sub, group.by = "IMM_IL15_annotation.res0.6.presubset",label = F) + labs(title = 'IMM_IL15_annotation.res0.6.presubset'))| (DimPlot(IMM_T2T3, group.by = "RNA_snn_res.0.7", label = T, repel = T)+ labs(title = 'RNA_snn_res.0.6')) )/((DimPlot(IMM_T2T3.sub, group.by = "IMM_IL15_annotation.res0.6.short2") + labs(title = 'IMM_IL15_annotation.res0.6.short2'))| (DimPlot(IMM_T2T3, group.by = "IMM_IL15_annotation.res0.6.short2", label = F, repel = T)+ labs(title = 'IMM_IL15_annotation.res0.6.short2')) )
```           

## Overlay annotation confidence scores from presubset object to sub object to see if small clusters are low confidence 
```{r read library mapping results}
mapping <- read.csv("/Users/brakeam/Library/CloudStorage/OneDrive-NationalInstitutesofHealth/JP & Alexis/20240419_newDTA/6_AnalysisOutput/IMM/MapMyCells/IMM_T2T3_10xWholeMouseBrain(CCN20230722)_HierarchicalMapping_UTC_1722307615263/IMM_T2T3_10xWholeMouseBrain(CCN20230722)_HierarchicalMapping_UTC_1722307615263.csv",comment.char="#")
head(data.frame(mapping))

```
```{r define modified mapping, warning=FALSE}
# Assign rare classes and subclasses as "other"
mapping$class_new <- mapping$class_name
 mapping$class_new[!is.element(mapping$class_name,names(head(-sort(-table(mapping$class_name)),5)))] = "other"
 mapping$class_new[which(mapping$class_bootstrapping_probability <.70)] = "Probability < 0.70"

mapping$subclass_new <- mapping$subclass_name
mapping$subclass_new[!is.element(mapping$subclass_name,names(head(-sort(-table(mapping$subclass_name)),20)))] = "other"
mapping$subclass_new[which(mapping$subclass_bootstrapping_probability <.70)] = "Probability < 0.70"

mapping$supertype_new <- mapping$supertype_name
mapping$supertype_new[!is.element(mapping$supertype_name,names(head(-sort(-table(mapping$supertype_name)),6)))] = "other"
mapping$supertype_new[which(mapping$supertype_bootstrapping_probability <.70)] = "Probability < 0.70"

# Put row.names as data colnames and the order to match the data
rownames(mapping) <- mapping$cell_id
mapping <- mapping[colnames(IMM_T2T3.sub@assays[["RNA"]]@counts),]

# Create the Seurat object
dataSeurat <- IMM_T2T3.sub
dataSeurat@meta.data <- cbind(IMM_T2T3.sub@meta.data,mapping)
```   
```{r fig.height=4, fig.width=9}
FeaturePlot(dataSeurat,features = c('class_bootstrapping_probability'),cols = c("#ae2012",'grey90'),blend= F, pt.size = 0.2) &NoAxes() | FeaturePlot(dataSeurat,features = c('subclass_bootstrapping_probability'),cols = c("#ae2012",'grey90'),blend= F, pt.size = 0.2) &NoAxes()
```
```{r fig.height=4, fig.width=10}
DimPlot(dataSeurat, group.by="subclass_new", label=F, repel = T, ncol = 1, pt.size =.25) + NoAxes() 
```
